%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\usepackage{hyperref}
\hypersetup{colorlinks=false}
 
\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Max Kovalovs} % Your name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
 
\moveleft.5\hoffset\centerline{\llap{\href{mailto:max@maxkovalovs.us}{max@maxkovalovs.us} $\cdot$ }\href{https://github.com/max-kov}{github.com/max-kov}\rlap{ $\cdot$ \href{https://linkedin.com/in/max-kov}{linkedin.com/in/max-kov}}}

%----------------------------------------------------------------------------------------

\begin{resume}

\section{EDUCATION}

{\sl Imperial College London,} Computer Science \hfill 2018 to 2021\\
Penultimate year student. Completed first year with a first.
 
\section{EXPERIENCE}

{\sl Software Engineer Intern} \hfill Summer 2019\\
Gearset Limited, Cambridge, UK

\begin{itemize} \itemsep -2pt % Reduce space between items
    \item Worked with functional javascript to add a dynamic task filter using Knockout JS, lodash and Squire.
    \item Worked with C\# and github API to show whether a branch could be deployed into in the app.
\end{itemize}
 
{\sl Software Engineer Intern} \hfill Summer 2018\\
\href{https://www.tngtech.com/en.html}{TNG Technology Consulting GmbH}, Munich, Germany

\begin{itemize} \itemsep -2pt
	\item Developed a REST API with Flask for working with a large set of legal documents.
    \item Created a continuous integration pipeline with Jenkins, tox and pytest.
    \item Designed a normalised multi-table database schema to store document information.
    \item Dockerised the application for easy deployment.
    \item Developed a front end for uploading documents into the system.
    \item Performed data analysis of the legal document dataset using Pandas.
    \item Acquired experience working in agile teams, writing good tests, presenting and talking to clients.
\end{itemize}

\section{PROJECTS}

{\sl Pool Game} \hfill \href{https://github.com/max-kov/pool}{github.com/max-kov/pool}\\
A 2d top-down pool game written in python.

\begin{itemize} \itemsep -2pt
\item Realistic ball collisions based on Newtonian mechanics.
\item Code analysis and testing pipelines with CodeClimate and TravisCI.
\item Custom 3d ball rendering.
\end{itemize}

{\sl The Archived}\hfill \href{https://maxkovalovs.us}{maxkovalovs.us}\\
Personal blog on programming-related topics.

\begin{itemize} \itemsep -2pt
\item Written in RMarkdown (Blogdown).
\item Seamless compilation and deployment with TravisCI.
\item Hosted on GitHubPages.
\end{itemize}

\section{EXTRA-CURRICULAR} 

{\sl Progmeistars} \hfill 2013 to 2016\\
Took several programming courses at Progmeistars computer science school, where I learned the basics.

\begin{itemize}
\item Did courses on graphics, OOP, algorithms and low level programming in C.
\item Was a part of a junior IOI team. We participated in many solo and team events. To prepare for Olympiads we had weekly lessons where we've covered computer science topics like big $\mathcal{O}$ notation, sorting algorithms and trees.
\end{itemize}

\end{resume}
\end{document}