---
title: Testing python applications with Pytest.
author: Max Kovalovs
date: '2018-07-28'
slug: testing-python-applications-with-pytest
categories: [python]
tags: []
output:
  blogdown::html_page:
    toc: true
---

# Asserting Errors

```{r engine='bash', comment='', echo=FALSE}
cat testing-python-applications-with-pytest/test_zerodiv.py
```

```{r engine='bash', comment='', echo=FALSE}
pytest testing-python-applications-with-pytest/test_zerodiv.py -vv || true
```

# Fixtures

A fixture is an object that is constructed specifically for the test and is passed as one of the parameters to the test. For example, you could create and return a database connection in a fixture, use it in a test and then close it in the fixture when the *scope* is closed. More [here](https://docs.pytest.org/en/latest/example/simple.html).

# Patching

Mocks allow you to replace parts of your production system (which is being tested) with mock objects and make assertions about how they have been used or make them return specified values. Pytest has a very neat fixture plugin called [pytest-mock](https://github.com/pytest-dev/pytest-mock), which uses builtin `unittest` module but wraps it in a pytest fixture, removing the annotation boilerplate and almost makes it look like magic. The `patch` in `unittest` decorator allows you to specify which object we are going to replace with a mock. With `pytest-mock` the process looks like this:

* Testing target

```{r engine='bash', comment='', echo=FALSE}
cat testing-python-applications-with-pytest/depth_counter1.py
```

* Testfile

```{r engine='bash', comment='', echo=FALSE}
cat testing-python-applications-with-pytest/test_patch1.py
```

```{r engine='bash', comment='', echo=FALSE}
pytest testing-python-applications-with-pytest/test_patch1.py -vv || true
```

The `mocker` argument is actually a Mock module fixture, provided by `pytest-mock` (can be seen in function parameters). Pytest has several of those standard builtin fixtures which you can access in any test, to see all of the ones you have installed run:

```
pytest -q --fixtures
```

## Tricky imports

Consider this example:

* Testing target

```{r engine='bash', comment='', echo=FALSE}
cat testing-python-applications-with-pytest/depth_counter2.py
```

* Testfile

```{r engine='bash', comment='', echo=FALSE}
cat testing-python-applications-with-pytest/test_patch2.py
```

```{r engine='bash', comment='', echo=FALSE}
pytest testing-python-applications-with-pytest/test_patch2.py -vv || true
```

Python veterans who know how python imports work, will realise that by importing using the `from` keyword, the testing file will have it's own copy of the function, thus patching `os.getcwd` doesn't do anything and patching `depth_counter2.py` does.


# Mocks

Mocks don't have to strictly substitute functionality in the testing function, they can also be passed as regular arguments:

```
from mock import Mock

class TestRegister:
    def test_under_18(self, mocker):
        form = Mock()
        form.age = "17"

        assert not validate_age(form)
```

Here, instead of making a complicated form object with user data, we just make a mock that will have only the values that will be tested.

# Parametrization

If you have loads of tests that run the same code on different input you can parametrize the tests:

```{r engine='bash', comment='', echo=FALSE}
cat testing-python-applications-with-pytest/test_parametrised.py
```

```{r engine='bash', comment='', echo=FALSE}
pytest testing-python-applications-with-pytest/test_parametrised.py -vv || true
```

When you run `pytest --verbose` the test id string will be printed along with the string. Still, different groups of tests should be grouped together in different test functions or test classes.

