---
title: Assert vs raise
author: Max Kovalovs
date: '2018-09-20'
slug: assert-vs-raise
categories: ["python"]
tags: []
---

# Intro

In a perfect world nobody would need exceptions in their programs, however, often unexpected things happen during runtime - invalid values get submitted, users make typos when writing paths and so on. To handle this developers use exceptions - upon encountering an abnormal situation (e.g. division by zero) the normal execution flow is interrupted, until the exception is dealt with. In python, doing this would look like this:


```{r engine='bash', comment='', echo=FALSE}
cat assert-vs-raise/pizza_slice_raise.py
```

```{r engine='bash', comment='', echo=FALSE}
python assert-vs-raise/pizza_slice_raise.py || true
```

However, python has assertion statements, which do a similar thing:

```{r engine='bash', comment='', echo=FALSE}
cat assert-vs-raise/pizza_slice_assert.py
```

```{r engine='bash', comment='', echo=FALSE}
python assert-vs-raise/pizza_slice_assert.py || true
```


# Differences

Both keywords are used to raise an exception but there are some key differences:

 - `assert` cannot specify the type of the error raised, it will always raise `AssertionError`.
 - As a result of the previous point, `assert` statements become more readable because they only take one line of code.
 - `assert` statements can be fully disabled during runtime using the `-O` flag a.k.a. the optimise mode.

# Use cases

In computer programming, assertions have a special meaning - an expression that is assumed or asserted to be true. Therefore, programmers usually use assertions to state the conditions that are *required* to be true for the program to run. However, if a user submitted a wrong path to the required file, even though the program cannot execute further, we only need to ask the user to check and correct the submitted path, hence a `raise FileNotFoundError` would be more appropriate.

On the other hand, if our function received a string instead of an integer as one of its inputs, we cannot recover because receiving an integer is one of the requirements for the procedure to run.

# Conclusion

`assert` statements could be used effectively to describe the expected input/conditions of the function during development time, due to their smaller code size comparing to `raise` statements. However, assertions should only be used for debugging during development time, not only because they can be disabled with the `-O` flag, but also because production code should be tested and all conditions that could cause an error should be handled during input validation.

`assert` statements should never be used for input validation and to detect other predictable errors during runtime, they should be handled with `raise` statements.

